Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-08 ms/manuscript.Rmd
Update MS
- Use some overly-complicated code to report same vs. different p-value for MPDfunc vs. MNTDfunc

# Calculate mean richness by growth habit
mean_rich <-
  div_metrics_all %>%
  group_by(habit) %>%
  summarize(
    mean_rich = mean(ntaxa) %>% round_t(1),
    sd_rich = sd(ntaxa) %>% round_t(1)
  ) %>%
  mutate(stat = glue("{mean_rich} ± {sd_rich}"))
```

@@

We observed a total of `r traits_with_abun %>% filter(abundance > 0) %>% pull(species) %>% n_distinct` species across all plots, including `r n_epi` epiphytic and `r n_ter` terrestrial species.
Mean species richness was `r mean_rich %>% filter(habit == "epiphytic") %>% pull(stat)` \si{\species}per plot for epiphytes and `r mean_rich %>% filter(habit == "terrestrial") %>% pull(stat)` \si{\species} per plot for terrestrial species (not significantly different; two-sided \tval-test, \pval = `r get_mod_result(t_test_print, "ntaxa", "p")`; \fig \@ref(fig:comm-div)).
Species richness increased with elevation for both epiphytes and terrestrial communities (\fig \@ref(fig:comm-div)).
Epiphytic communities were more diverse than terrestrial ones as measured by both MPD~func~ and MNTD~func~ (two-sided \tval-test, \pval `r get_mod_result(t_test_print, "mpd.obs.z.func", "p")` and `r get_mod_result(t_test_print, "mntd.obs.z.func", "p")`, respectively).
Functional diversity increased along the gradient for both terrestrial and epiphytic communities when measured with MPD~func~ (linear model, \rval^2^ = `r get_mod_result(model_summ_print, "mpd.obs.z.func", "r")`, \pval `r get_mod_result(model_summ_print, "mpd.obs.z.func", "p")`), but not MNTD~func~.
Epiphytic communities were more phylogenetically clustered than terrestrial communities overall when measured using MNTD~phy~ (two-sided \tval-test, \pval `r get_mod_result(t_test_print, "mntd.obs.z.phy", "p")`) but not MPD~phy~ (\pval = `r get_mod_result(t_test_print, "mpd.obs.z.phy", "p")`; \fig \@ref(fig:comm-div)).
No significant trend was detected in phylogenetic community structure with elevation in either terrestrial or epiphytic communities (\fig \@ref(fig:comm-div)).

>>>>

# Calculate mean richness by growth habit
mean_rich <-
  div_metrics_all %>%
  group_by(habit) %>%
  summarize(
    mean_rich = mean(ntaxa) %>% round_t(1),
    sd_rich = sd(ntaxa) %>% round_t(1)
  ) %>%
  mutate(stat = glue("{mean_rich} ± {sd_rich}"))

# Do some special formatting for reporting rounded MPDfunc vs MNTDfunc P-val
# - combine into a single value if same, or report each different value with 
# "respectively" if different
if(
  magrittr::equals(
    t_test_print %>%
      filter(var == "mpd.obs.z.func") %>%
      pull(p),
    t_test_print %>%
      filter(var == "mntd.obs.z.func") %>%
      pull(p)
  )
) {
  p_mpd_func_mntd_func <- get_mod_result(t_test_print, "mpd.obs.z.func", "p")
  both <- "both "
} else {
  p_mpd_func_mntd_func <- paste0(
    get_mod_result(t_test_print, "mpd.obs.z.func", "p"),
    " and ",
    get_mod_result(t_test_print, "mntd.obs.z.func", "p"),
    ", respectively"
  )
  both <- ""
}
```

@@

We observed a total of `r traits_with_abun %>% filter(abundance > 0) %>% pull(species) %>% n_distinct` species across all plots, including `r n_epi` epiphytic and `r n_ter` terrestrial species.
Mean species richness was `r mean_rich %>% filter(habit == "epiphytic") %>% pull(stat)` \si{\species} per plot for epiphytes and `r mean_rich %>% filter(habit == "terrestrial") %>% pull(stat)` \si{\species} per plot for terrestrial species (not significantly different; two-sided \tval-test, \pval = `r get_mod_result(t_test_print, "ntaxa", "p")`; \fig \@ref(fig:comm-div)).
Species richness increased with elevation for both epiphytes and terrestrial communities (\fig \@ref(fig:comm-div)).
Epiphytic communities were more diverse than terrestrial ones as measured by both MPD~func~ and MNTD~func~ (two-sided \tval-test, `r both`\pval `r p_mpd_func_mntd_func`).
Functional diversity increased along the gradient for both terrestrial and epiphytic communities when measured with MPD~func~ (linear model, \rval^2^ = `r get_mod_result(model_summ_print, "mpd.obs.z.func", "r")`, \pval `r get_mod_result(model_summ_print, "mpd.obs.z.func", "p")`), but not MNTD~func~.
Epiphytic communities were more phylogenetically clustered than terrestrial communities overall when measured using MNTD~phy~ (two-sided \tval-test, \pval `r get_mod_result(t_test_print, "mntd.obs.z.phy", "p")`) but not MPD~phy~ (\pval = `r get_mod_result(t_test_print, "mpd.obs.z.phy", "p")`; \fig \@ref(fig:comm-div)).
No significant trend was detected in phylogenetic community structure with elevation in either terrestrial or epiphytic communities (\fig \@ref(fig:comm-div)).
